High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-23 doc/asplos2013/results.tex
put all bulk synchronous figures into a single figure

Figures~\ref{fig:cktbulk}, \ref{fig:fluidbulk}, and \ref{fig:amrbulk} compare
the performance of the bulk-synchronous implementations versus the original
implementations for Circuit, Fluid, and AMR respectively.  Each plot contains
performance curves for both implementations on two different problem sizes.
Circuit is a compute-bound application and the bulk-synchronous implementation
performs reasonably well.  By 16 nodes however the overhead grows to 19\%
and 22\% on the small and large inputs respectively.  The Fluid application 
has a more evenly balanced computation-to-communication ratio.  As a result,
Fluid performance suffers significantly more by switching to
a bulk-synchronous model.  At 16 nodes, performance is 135\% and 52\% worse
than the original Legion implementations on the small and large problem sizes
respectively.  Finally, the AMR application is a memory bound application, and on 16 nodes
the bulk-synchronous version is 82\% and 102\% slower on the small and
large problem sizes.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{figs/circuit_bulk_sync.pdf}
\end{center}
\vspace{-6mm}
\caption{Circuit Bulk-Synchronous Performance.\label{fig:cktbulk}}
\vspace{-4mm}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{figs/fluid_bulk_sync.pdf}
\end{center}
\vspace{-6mm}
\caption{Fluid Bulk-Synchronous Performance.\label{fig:fluidbulk}}
\vspace{-4mm}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.33]{figs/amr_bulk_sync.pdf}
\end{center}
\vspace{-6mm}
\caption{AMR Bulk-Synchronous Performance.\label{fig:amrbulk}}
\vspace{-4mm}
\end{figure}

>>>>

Figure~\ref{fig:bulksync} compare
the performance of the bulk-synchronous implementations versus the original
implementations for Circuit, Fluid, and AMR respectively.  Each plot contains
performance curves for both implementations on two different problem sizes.
Circuit is a compute-bound application and the bulk-synchronous implementation
performs reasonably well.  By 16 nodes however the overhead grows to 19\%
and 22\% on the small and large inputs respectively.  The Fluid application 
has a more evenly balanced computation-to-communication ratio.  As a result,
Fluid performance suffers significantly more by switching to
a bulk-synchronous model.  At 16 nodes, performance is 135\% and 52\% worse
than the original Legion implementations on the small and large problem sizes
respectively.  Finally, the AMR application is a memory bound application, and on 16 nodes
the bulk-synchronous version is 82\% and 102\% slower on the small and
large problem sizes.

@@

\begin{figure}[h!]
\centering
\subfigure[Circuit Application]{
\label{fig:cktbulk}
\includegraphics[scale=0.33]{figs/circuit_bulk_sync.pdf}
}

\subfigure[Fluid Application]{
\label{fig:fluidbulk}
\includegraphics[scale=0.33]{figs/fluid_bulk_sync.pdf}
}

\subfigure[AMR Application]{
\label{fig:amrbulk}
\includegraphics[scale=0.33]{figs/amr_bulk_sync.pdf}
}
\vspace{-4mm}
\caption{Bulk-Synchronous Performance.\label{fig:bulksync}}
\vspace{-4mm}
\end{figure}
